A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2020-08-25 new-paper.Rmd
clarify point on 50 hectares paper

Do not deposit data in local file storage that does not provide DOI or accession numbers. For example, [@50Hectares] is hosted on a university server and accessed via FTP. It is not possible to effectively provide effective provenance and credit.

>>>>

Do not deposit data in local file storage that does not provide DOI or accession numbers. For example, [@50Hectares] was hosted on a university server and only accessible via a FTP server since 1982. It was not possible to easily access or cite the data without an explicit authorship agreement among other conditions. Only recently were the complete dataset deposited in Dryad without such conditions [@condit-2019].
